---
title: "PSY 8960 Week 8 Project"
author: "Anthony Greco"
date: "`r Sys.Date()`"
output: html_document
runtime: shiny
---

# **Reproducible Image and Online Resources**
An image of this project as of *`r Sys.Date()`* can be accessed by [clicking this link](link url).
An interactive web app is available by [clicking this link instead.](link url)

# **Script Settings and Resources**
```{r setup, echo = TRUE, results='hide'}
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
library(tidyverse)
library(shiny)
```

# **Data Import and Cleaning**
Data cleaned to recast condition and gender as factors, timestamps as POSIX, reverse code q5, and create mean values of q1:q6 and q7:q10. This makes the tibble easier to interpret, more consistent, and coded accurately for future analyses and visualizations. Past data cleaning efforts beyond this scope (dropping all cases that did not answer 1 on q6) were not included because they were noted in this project. 
```{r setup}
week8_tbl <- read_csv(file ="../data/week3.csv") %>%
  mutate(condition = factor(condition, levels = c("A", "B", "C"), labels = c("Block A", "Block B", "Control")),
         gender = factor(gender, levels = c("M", "F"), labels = c("Male", "Female")),
         q5 = case_match(q5, 1 ~ 5, 2 ~ 4, 3 ~ 3, 4 ~ 2, 5 ~ 1),
         timeStart = ymd_hms(timeStart),
         q1_q6_mean = rowMeans(across(q1:q6)),
         q7_q10_mean = rowMeans(across(q7:q10))
  )
```

# **Visualization**
```{r echo = FALSE} 
select(week8_tbl, q1:q6)

ggplot(week8_tbl, aes(x = q1_q6_mean, y = q7_q10_mean)) +
  geom_smooth(method = "lm", color = "purple", se = TRUE) +
  geom_point()

```